\chapter*{Acknowledgements}
\pageauthor{Helena Adam}
We want to thank a lot of people. On the one hand, those people, who made it possible for us to attend the \gls{htbla} Kaindorf. On the other hand, those who contributed valuable help to create a successful diploma thesis.

We are full of thankfulness to all employees of our partner company, Sunlime IT Services GmbH, who supported us in our work. Special thanks go to our employer DI Dominik Fuchshofer, who gave us the chance to do our diploma thesis with his company. As contact person he always stood at our side whenever we needed assistance. Without his tireless input, patience and understanding it would not have been possible to complete our diploma thesis successfully.

Furthermore, we would like to thank DI Dr. Wolfgang Pölzleitner and DI Florian Schreiber, who took over the role supervising teachers. When we had problems or other blockades, they always were there to help us finding a solution and make the best out of it. Through their cheerful character and their enthusiastic interest in our work, we  even enjoyed the meetings and project follow-ups.

Then, we want to thank our head teacher Mrs. Mag. Michaela Primig, who supported us during our career at \gls{htbla} Kaindorf. Sometimes it was not that easy for her to understand our attitudes, but then, she never lost hope that we would  finally cope.

Last but not least, our deep thankfulness needs to be expressed to our parents. They supported us during our \gls{htbla} career and provided motivational help whenever needed. Finally special thanks go to Paul's dad, who helped us a lot with our diploma thesis.
\clearpageauthor

