\chapter*{Foreword from the Employer}
Kilometre allowance and the documentation of driven kilometres for the company are important todos for every self employed entrepreneur. The fact is that writing every business car ride into an excel sheet or manually into a car log book is really annoying. It would be much more convenient if a device in my business car logs every trip and I am able to define my car rides via a web portal afterwards. This was the idea behind “Log book” which we wanted to test drive with our friends at HTBLA Kaindorf/Sulm. Next to the hardware prototype it was also important to get an idea for a possible database solution. To understand the project better we provided a design proposal next to the hardware to sum up the first section of the project.

But more important than the final outcome of the project is to see how young people are able to come up with new and interesting ideas and dive into project related subtasks which have to be accomplished. It is also great to transfer some of the know-how we have worked out and to see how these ideas are adopted and developed for the project.

I am sure that every project member is able to take something from this diploma thesis and use it for their own future business life. I wish Helena, Laura, Claudio and Paul the very best for the final exams. You are going to rock the stage.

  Best,\newline
Dominik\newline\newline
DI Dominik Fuchshofer, BSc\newline
CEO/CTO at Sunlime IT Services GmbH\newline
February 2016
